Coherent optical association of single molecules

### 2020-09-17 paper.tex
WIP: result analysis

In order to understand the fidelity of molecule formation, we fit our measurements to a model that includes a Raman Rabi frequency and a finite lifetime for the final molecular state. We also account for atomic state loss by measuring the single and two body lifetime for the atomic state (figure ...). The result suggests that our transfer has a Raman Rabi frequency of and the molecule we form has a lifetime of $...$. We can also directly verify this result by measuring the lifetime of the molecule directly. This is done by applying a reverse Raman pulse to dissociate the molecule back to atoms after a variable wait time. The result of the direct measurement shows a molecular lifetime consistent with our fitting of the Raman transition data.

>>>>

In order to understand the fidelity of molecule formation, we fit our measurements to a model that includes a Raman Rabi frequency and a finite lifetime for the final molecular state (figure 3...). The effect due to atomic state loss was taken into account by measuring the single and two body lifetime of the atoms directly (figure 3...). The fit shows that we have a Raman Rabi frequency of $...$. The molecule we form has a lifetime of $...$ which is the main limitation on the fidelity of the transfer. The molecule lifetime can be verified directly by adding a second Raman pulse to dissociate the molecule back to atoms after a variable wait time (figure 3...). The result shows a molecular lifetime consistent with our fitting of the Raman transition data.

The ratio of molecule scattering rate and the Rabi frequency is larger than the theory prediction.
In order to understand the origin of this discrepancy, we measured the dependency of the Raman resonance as a function of the tweezer power and frequency. The important results from the fits are resonance frequency (light shift), Raman Rabi frequency, atomic lifetime and molecular lifetime, each provide us information about a different combination of physical processes.

First we look at the change in resonance frequency. As a function of the tweezer power, we observed a linear dependency on the resonance frequency caused by the differential light shift between the atomic and molecular state (figure ?). When we vary the tweezer frequency around the $v=0$ excited state, we can further observe a $1/\delta$ component and a background component that is constant for different detunings. The background is caused by coupling to all the other excited states that are further away which is not very important in this case. The $1/\delta$ component, however, is due to the coupling to the $v=0$ excited state and from equation (?) we know that this is mainly due to the coupling between the excited and ground molecular states. From this, we can calculate a down leg matrix element of $....$ which is similar to what we calculated from theory (ref/sm theory). (make sure theory part mentions $\Omega_{down}\gg\Omega_{up}$, also $\Omega$ vs $\Omega'$ for the single leg vs cross coupling number).

(talk about blue side?)

The Raman Rabi frequency shows a non-linear dependency on the tweezer power due to the change in the atomic wavefunction caused by the change in confinement. The up leg matrix element scales with the short length atomic wavefunction amplitude which is 0.375 for weakly interaction particles. However, due to the strong interaction between the two atoms, this approximation breaks down. Instead, theory calculation shows that the scaling is very well approximated by a power of 0.29 within the range of confinement in our experiment. Combined with the intensity factor of the Raman beams, the Raman Rabi frequency should scale with 1.29 power of the tweezer intensity, which agrees with our experimental result. Similar to the light shift, there is also a background component and a $v=0$ component in the Raman Rabi frequency. The $v=0$ component predicts a up leg Rabi frequency of $...$ which is consistent with theory. Unfortunately, the background Raman Rabi frequency cancels the Rabi frequency for red detuning Raman transition which is one of the factors that decreases our transfer efficiency. (need blue side?)

% Parameters: Light shift, Rabi frequency, atomic scattering rate, molecular scattering rate
% Variables: detuning, power
% Changes: background, single line
